---
title: "p8105_hw1_ys3637"
output: github_document
date: "2022-09-24"
---

```{r}
# library all packages that we need at the beginning
library(ggplot2)
library(tidyverse)
```

## Problem 1

```{r}
# load data set penguins.
data("penguins", package = "palmerpenguins")
# print out the first several lines of the data and we see it has 8 variables:
# species of penguins (factor), island (factor), bill length in mm (double),
# bill depth in mm (double), flipper_length_mm (integer), body_mass_g (integer),
# sex of penguins (factor), year (int).
head(penguins)
# to find the size of the dataset.
# we can tell penguins dataset has 344 rows and 8 cols.
nrow(penguins)
ncol(penguins)
# the mean of flipper length is 200.9 mm
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

Therefore, we can tell in dataset penguins, it has 8 variables: species of penguins (factor), island (factor), bill length in mm (double), bill depth in mm (double), flipper_length_mm (integer), body_mass_g (integer), sex of penguins (factor), year (int). And the size of the dataset is 344 rows and 8 columns, while the mean of flipper length is 200.9 mm, not including NA.

```{r}
# create a scatterplot of flipper_length_mm (y) vs bill_length_mm (x)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
# save the scatter plot file to the project
ggsave("penguins_scatter_plot_of_flipper_vs_bill.pdf", height = 4, width = 6)
```

## Problem 2

```{r}
# create a dataframe
df = 
  tibble(
    random_N = rnorm(n = 10),
    logical = random_N > 0,
    char = c("a", "a", "a", "b", "b", "b", "c", "c", "c", "c"),
    fac = factor(char, levels = c("a", "b", "c"))
  )
# print out the dataframe
df
```

```{r}
# take the mean of each variable in a dataframe
# the mean of random_N is 0.72
df %>%
  pull(random_N) %>%
  mean()
# the mean of the logical is 0.6
df %>%
  pull(logical) %>%
  mean()
# the mean of the char is NA, not applicable
df %>%
  pull(char) %>%
  mean()
# the mean of the fac is NA, not applicable
df %>%
  pull(fac) %>%
  mean()
```

From the above, we can see that both random_N and logical variables have a mean--mean of random_N is 0.72 and mean of logical is 0.6--but neither char nor fac has a mean.


